Constructing a universe for the setoid model

### 2020-07-08 paper.tex
last minute updates

Finally, we will assume an identity type in the style of Martin-L\"of's
inductive identity type. The main difference is that our identity type is a
$\mProp$-valued relation. We also include a transport combinator
\textsf{transp}.
%
\begin{align*}
  & \textsf{Id} : \{A : \mType \} \to A \to A \to \mProp \\
  & \textsf{refl} : \{A : \mType \} (a : A) \to \textsf{Id}\ a\ a \\
  & \textsf{transp} : \{A : \mType \} (C : A \to \mType) \{a_0\ a_1 : A\} \to \textsf{Id}\ a_0\ a_1 \to C\ a_0 \to C\ a_1
\end{align*}

The \textsf{transp} combinator provides a strong elimination principle allowing
to eliminate a strict proposition (the identity type) into arbitrary types.
%
The reason to have an identity type in $\mProp$ with such a strong transport
rule are made clear in Section~\ref{inductive-universe}.
%
% Note that this identity type must necessarily be assumed as
% primitive; in fact, even though we could have defined \textsf{Id}
% from $W_\mProp$, \textsf{transp} is not definable from $W_\mProp$
% elimination.

>>>>

Finally, we will assume an identity type in the style of Martin-L\"of's
inductive identity type. The main difference is that our identity type is a
$\mProp$-valued relation. We have a transport combinator
\textsf{transp} from which \textsf{J} is derivable.
%
\begin{alignat*}{10}
  & \textsf{Id} && :\,\, && \{A : \mType \} \to A \to A \to \mProp \\
  & \textsf{refl} && : && \{A : \mType \} (a : A) \to \textsf{Id}\ a\ a \\
  & \textsf{transp} && : && \{A : \mType \} (C : A \to \mType) \{a_0\ a_1 : A\} \to \textsf{Id}\ a_0\ a_1 \to C\ a_0 \to C\ a_1 \\
  & && && \textsf{transp}\ C\ \{x\}\ \{x\}\ e\ u \equiv u
\end{alignat*}

The \textsf{transp} combinator provides a strong elimination principle allowing
to eliminate a strict proposition (the identity type) into arbitrary types.
%
We only use this identity type with such a strong transport in Section~\ref{inductive-universe}.
%
% Note that this identity type must necessarily be assumed as
% primitive; in fact, even though we could have defined \textsf{Id}
% from $W_\mProp$, \textsf{transp} is not definable from $W_\mProp$
% elimination.
